Proposed Solution

### 2017-04-18 OOPSLA17/secs/intro.tex
autocommit

In order to learn a specification from this large set of configuration
files,
the first step is to 
translate the training set into a more structured typed representation.
We then apply our learning process to learn an abundant set of rules 
specifying various properties that hold on the given training set. 
The learning process is a more expressive form of association rule learning~\cite{agrawal1993mining}, which is used to learn predicate relations between multiple keywords in a configuration file.
The rules, in general, specify which properties such as, one kewyord must appear before another, or the value of one keyword should always be greater than another.

The learning process is language-agnostic and works for any kind 
of configuration files, though all of the files in the training set need to be of 
the same language (such as MySQL or HTTPD configuration files).

This learning process is a way of deriving a specification for configuration files. 
With the learned specification, \app can then efficiently check 
the correctness of the configuration files of interest and detect 
potential errors.

The errors that \app detects may cause total system failures, but can also be more insidious, for example slowing down the system only when the server load increases beyond a certain threshold.
Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging 
technique~\cite{Zeller:2005:WPF:1077048} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.

@@

\ruzica{hmmm... this appears to be repeating - can you merge some of those stuff with stuff above}

Our learning algorithm surmounts both of these shortcomings present in 
existing tools.  \app implements a learning
algorithm inspired by {\em association rule
learning}~\cite{agrawal1993mining} that analyzes a training set of partially correct files.
A file in the training set might contain several different errors, but errors only appear 
in a small percentage of files. 
We first translate those file into an intermediary typed language.
\app then learns rules based on the inferred types of the keywords from the training set.
However, since the files might also contain errors we take 
this into account when learning correct rules. All learned rules are 
annotated with the probability of correctness.  
To ensure the learned rules are correct enough,
\app employs a graph analysis to refine the set learned rules.
\app analyzes the rule graph to rank the importance and relevance of the learned rules.

>>>>

In order to learn a specification from this large set of configuration
files,
the first step is to 
translate the training set into a more structured typed representation.
We then apply our learning process to learn an abundant set of rules 
specifying various properties that hold on the given training set. 
The learning process is a more expressive form of \textit{association rule learning}~\cite{agrawal1993mining}, which is used to learn predicate relations between multiple keywords in a configuration file.
The rules, in general, specify which properties such as, one keyword must appear before another, or the value of one keyword should always be greater than another.
This set of learned rules constitutes a specification for a correct configuration file,
which are then used to efficiently check the correctness of a user's configuration files and detect 
potential errors. 
The learning process is language-agnostic and works for any kind 
of configuration files, though all of the files in the training set need to be of 
the same language (such as MySQL or HTTPD configuration files).

Our implementation, \app, detects errors that may cause total system failures, but can also find more insidious errors, for example configurations that will slow down the system only when the server load increases beyond a certain threshold.
Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging techniques~\cite{Zeller:2005:WPF:1077048} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.

@@

Our learning algorithm surmounts both of these shortcomings present in 
existing tools. \app implements a learning
algorithm inspired by association rule
learning~\cite{agrawal1993mining} that analyzes a training set of partially correct files.
A file in the training set might contain several different errors, but errors only appear 
in a small percentage of files. 
We first translate those file into an intermediary typed language.
\app then learns rules based on the inferred types of the keywords from the training set.
However, since the files might also contain errors we take 
this into account when learning correct rules. All learned rules are 
annotated with the probability of correctness.  
To ensure the learned rules are correct enough,
\app employs a graph analysis to refine the set learned rules.
\app analyzes the rule graph to rank the importance and relevance of the learned rules.
